---
title: "data_structure"
author: '2015122016'
date: "2019년 4월 4일"
output: html_document
editor_options: 
  chunk_output_type: console
---
```{r include=F}
library(tidyverse)
library(DT)
```

#Introduction
data structure (x)     
data_structure (o)     
data-structure (o)     
DataStructure  (o)     
<- let naming consistency 

1. try 'knit' before writing the main contents

option not to make the extra folder to save the images like graphs
: "self_contained: true"

#자료구조
##Scalar
- 연속형
    - 자연수 integer
    - 실수 floating point
- 범주형
    - factor
    - 문자열 string

###Numeric

$$\text{BMI} = \frac{weight}{\left(height/100\right)^{2}}$$

$$\text{BMI} = \frac{\text{체중(Kg)}}{\text{키(m)}^{2}}$$

Using the equation above,

 브로카지수| BMI값 
-|:-:
 저체중 | < 18.5
 정상 체중 | 18.5 ~ 25.0 
 과체중 | 25.0 ~ 30.0 
 비만 | > 30.0 

* :-: 가운데정렬 

```{r integer}
height <- c(170, 180, 165)
weight <- c(50, 70, 85)
mean(height)
1.01*height

BMI <- weight / (height/100)^2 ; BMI
(BMI <- weight / (height/100)^2)

```

###Characteristic & Factor
```{r factor}
BMI_string <- c('저체중', '정상 체중', '비만')

BMI_factor <- factor(BMI_string, levels=c('저체중', '정상 체중', '과체중', '비만'))
#if there is no '과체중' -> as.factor(BMI_string) is also ok

as.numeric(BMI_string)
#but it is neccessary to check whether the gap between the levels is same 

BMI_mat <- rbind(BMI, BMI_string)
colnames(BMI_mat) <- c('A', 'B', 'C')
BMI_mat

length(BMI)
BMI_df <- data.frame("BMI"= BMI, "BMI_factor"=BMI_factor, "BMI_string"=BMI_string)
BMI_df
```

* useful packages for categorcal variables
- forcats (later)

* extra
- using in test mining
    - paste(BMI_string, "+")
    - paste(BMI_string, collapse = ",")



#외부 데이터 가져오기
```{r}
data <- tribble(
~'가명', ~'체중', ~'키', ~'재산',
'아이언맨', 70, 185, 1000,
'이기쁨', 48, 162, 1300,
'어피치', 40, 100, 999999999,
'무지', 20, 50, 999999999,
'뽀로로', 30, 50, 0,
'이상완', 100, 200,10000,
'곰돌이푸',20,85,1600000000000,
'B', 73.13, 183, 105,
'F', 45, 165, 10000000000000,
'YEAH', 170, 48, 10000,
'토르', 85, 185, 9999999999999,
'AA', 60, 100, 10000000,
'AAA', 76, 111, 10093,
'배수한', 180, 64, 1000,
'지현이', 46, 175, 1000000000000,
'응통', 50, 150, 7500,
'마라탕' ,1,30,12345678,
'금순이', 45, 156, 50000,
'이동석', 177, 68, 10000000000000,
'김원채',45,168,50000000,
'피카츄',100,50,1000000) 
summary(data)

work_data <- read.csv("clipboard")
#import the data copied on clipboard
#Awesome!!
summary(work_data)


dat <- read.csv("datdat.csv")
#memo에서 save as (name).csv
summary(dat)

library(tidyverse)

dt_df <- read_csv("data_fin.csv",
                       col_types = cols(
                            가명 = col_character(),
                            체중 = col_double(),
                            키 = col_double(),
                            재산 = col_double()
                          ))               
#function : read_csv  *** read.csv (X)
#encoding : UTF-8
 
model_df <- dat %>% mutate(rich = ifelse(dat[,4] > median(dat[,4]), 'rich', 'unrich')) %>%
  mutate(rich = factor(rich, levels=c('unrich', 'rich'))) %>%
  select(-가명)

model_df %>%
  DT::datatable()
```

*extra
- tribble() : make dataframe
- 전체 열 앞에 커서 : alt + scrolling
- 다중선택(drag) : Shift + 방향키 -> '' or () 사용 가능 



